Online {\IterComp}

### 2017-11-16 motivation.tex
adds some text for the new experiments

    \paragraph{Challenges of using real inputs online.} We could overcome the problems of representative inputs by just evaluating
    optimization sequences online while the application is being used. 
    %Optimization sequences are compared based on how much faster the program becomes.
    This gives us live data but creates a new problems.
    With live data, we cannot just compare runtimes. 
    When all of the optimization sequences are tested against the same inputs, it is just a matter of comparing runtimes.
    A shorter runtime for processing the same data means a more efficient binary.
    With live data, we cannot do this, each binary processes
    whatever the input happens to be. We need another efficiency metric that only requires a single use of an optimized binary with a
    single input.

@@

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose.
    \FIXME{Evidence1:}
    To show this, we performed iterative compilation guided by IPC for the same set of 10 inputs
    discussed in Figure~\ref{fig:motivation_wrong_inputs} and compare with the previous approach which optimizes directly for execution time.
    The best optimization sequence found in Figure~\ref{fig:motivation_wrong_inputs}
    has an average speedup of 1.7 over \texttt{-O3} and an average IPC of 2.59.
    However, iterative compilation guided by IPC is able to find an optimization
    sequence that produces a higher IPC of 2.72 but an average slowdown of 0.98.
    This result agrees with the known fact that higher IPC does not necessarily translate to lower execution time when comparing different versions of the program.
%     \FIXME{Evidence2:}
%    To show this, we ran
%    each of the \FIXME{32} \textit{KDataSets} benchmarks 1,000 times, each time with a different input \textit{and} a different optimized
%    binary, and we measured three metrics: runtime, inverse runtime, and IPC. \FIXME{Fig.XXX} shows the correlation coefficient between
%    them and a reasonable efficiency metric, speedup over \texttt{-O0}. For all benchmarks, the correlation coefficient is below
%    \FIXME{0.20} for runtime and below \FIXME{0.35} for inverse runtime. Both have obvious reasons for being inappropriate efficiency
%    metrics. Doubling the amount of data to be processed will cause the runtime to rise and the inverse runtime to fall, even if we use the same binary.
%    Efficiency has nothing to do with it. IPC also correlates poorly with efficiency, the correlation coefficient being just \FIXME{0.15}.
%    While it is used often in computer architecture, it works there because it is used with invariant binaries. In contrast, any compiler
%    optimization that trades high latency instructions for multiple low latency instructions can reduce IPC while improving efficiency.

>>>>

    \paragraph{Challenges of using real inputs online.} We could overcome the problems of representative inputs by just evaluating
    optimization sequences online while the application is being used. 
    %Optimization sequences are compared based on how much faster the program becomes.
    This gives us live data but creates a new problems.
    With live data, we cannot just compare runtimes. 
    When all of the optimization sequences are tested against the same inputs, it is just a matter of comparing runtimes.
    A shorter runtime for processing the same data means a more efficient binary.
    With live data, we cannot do this, each binary processes
    whatever the input happens to be. We need another efficiency metric that only requires a single execution of an optimized binary with a
    single input.

@@

    Typical single-run performance metrics, like runtime or Instructions Per Cycle~(IPC), are not fit for purpose.
    To show this, we performed iterative compilation executing each optimization sequence with a different input and then measuring both runtime and IPC.
    The experiments were performed in the set of inputs \#2 discussed in Figure~\ref{fig:motivation_wrong_inputs}.
    For the iterative compilation guided by runtime, it resulted on an average slowdown of 0.97 compared to \texttt{-O3}.
    For the iterative compilation guided by IPC, it resulted in an average slowdown of 0.51 with an IPC of 3.25., while the optimization expected with an average speedup of 1.07 has an average IPC of 2.31.
    This result agrees with the known fact that higher IPC does not necessarily translate to lower execution time when comparing different versions of the program.

%     \FIXME{Evidence2:}
%    To show this, we ran
%    each of the \FIXME{32} \textit{KDataSets} benchmarks 1,000 times, each time with a different input \textit{and} a different optimized
%    binary, and we measured three metrics: runtime, inverse runtime, and IPC. \FIXME{Fig.XXX} shows the correlation coefficient between
%    them and a reasonable efficiency metric, speedup over \texttt{-O0}. For all benchmarks, the correlation coefficient is below
%    \FIXME{0.20} for runtime and below \FIXME{0.35} for inverse runtime. Both have obvious reasons for being inappropriate efficiency
%    metrics. Doubling the amount of data to be processed will cause the runtime to rise and the inverse runtime to fall, even if we use the same binary.
%    Efficiency has nothing to do with it. IPC also correlates poorly with efficiency, the correlation coefficient being just \FIXME{0.15}.
%    While it is used often in computer architecture, it works there because it is used with invariant binaries. In contrast, any compiler
%    optimization that trades high latency instructions for multiple low latency instructions can reduce IPC while improving efficiency.

### 2017-11-16 results.tex
adds some text for the new experiments

>>>>

\subsubsection{Analysis of the cost during the online search}

We also evaluate the actual cost perceived by the user when applying online iterative compilation.
To this end we used the architecture described in Section~\ref{sec:oic-infra} with the search based on genetic algorithm.
The results suggest that the proposed approach can be profitable in real-world online scenarios.
For the \WCRelax-5\% configuration, an average speedup of XX was observed during the search, in the worst case with an slowdown of XX.
For the \WPRelax-5\% configuration, an average speedup of XX was observed during the search, in the worst case with an slowdown of XX.
